Reconstructing Propositional Proofs in Type Theory

### 2017-12-22 paper/sections/proof-reconstruction/resolve.tex
Paper (#59) : this closes #57, #56, #55, #58
* [ paper ] fixed intro in proof-reconstruction section.

* [ paper ] more spacing in metis table/strip rule begins section.

* [ paper ] formalization pattern with some fixes.

* [ paper ] minor fixes in type theory section.

* fixed some spacing issues.

* added footer to review paper.

* lots of changes.

* fixes for canonicalize section.

* minor fixes.

* minor fixes.

* removed redundacies and definitions.

* hypenation of Medellín.

* more info in some references.

* fixed some DOIs.

* minor fixes.

* [ paper ] diagram fixed.

* [ paper ] re

Logic equivalence between propositions is a major issue to justify
prover reasoning steps. Since we left out semantics to treat only the
syntax aspects of propositional logic, our approach shows logic
equivalence by converting propositions to their conjunctive normal
form, and reordering those and the inner disjunctions to match them.
Below, we provide Lemma~\ref{lem:reorder-or},
Lemma~\ref{lem:reorder-and}, Lemma~\ref{lem:reorder-and-or} to perform such reordering tasks, the omitted proofs can be found
in~\cite{AgdaMetis}.

@@

\begin{mainth}
  \label{thm:resolve}
  Let $ℓ$ be a literal, $ℓ : \Lit$, and $ψ : \Target$. If $Γ ⊢ φ₁$ and
  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$, where
  \begin{equation}
  \begin{split}
  \label{eq:resolve}
    &\fresolve : \Source \to \Source \to \Lit \to \Target \to \Prop\\
    &\fresolve~φ₁~φ₂~ℓ~ψ =
      \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
  \end{split}
  \end{equation}
\end{mainth}

@@

Continuing with the problem presented in
Example~\ref{ex:resolve-tstp}, we can use Theorem \ref{thm:resolve} to derive $Γ ⊢ p ∨ q$.

>>>>

Logic equivalence between propositions is a major issue to justify
prover reasoning steps. Since we left out semantics to treat only the
syntax aspects of propositional logic, our approach shows logic
equivalence by converting propositions to their conjunctive normal
form, and reordering those and the inner disjunctions to match them.

The \emph{negative normal form} of a formula is the logical
equivalent version of it in which negations appear only in the
literals and the formula does not contain any implications.

The \emph{conjunctive normal form} of a formula also called clausal
normal form is the logical equivalent version expressed as a
conjunction of clauses where a \emph{clause} is the disjunction of
zero or more literals.

Below, we provide Lemma~\ref{lem:reorder-or},
Lemma~\ref{lem:reorder-and}, Lemma~\ref{lem:reorder-and-or} to perform such reordering tasks, the omitted proofs can be found
in~\cite{AgdaMetis}.

@@

\begin{mainth}
  \label{thm:resolve}
  Let $ℓ$ be a literal, $ℓ : \Lit$, and $ψ : \Target$. If $Γ ⊢ φ₁$ and
  $Γ~⊢~φ₂$ then $Γ~⊢~\fresolve~φ₁~φ₂~ℓ~ψ$, where
  \begin{equation}
  \begin{split}
  \label{eq:resolve}
    &\fresolve : \Source \to \Source \to \Lit \to \Target \to \Prop\\
    &\fresolve~φ₁~φ₂~ℓ~ψ =
      \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
  \end{split}
  \end{equation}
\end{mainth}

@@

Continuing with the problem presented in
Example~\ref{ex:resolve-tstp}, we can use Theorem \ref{thm:resolve} to derive $Γ~⊢~p~∨~q$.
